---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(8675309)
```

# bfrr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/debruine/bfrr.svg?branch=master)](https://travis-ci.org/debruine/bfrr)
[![Codecov test coverage](https://codecov.io/gh/debruine/bfrr/branch/master/graph/badge.svg)](https://codecov.io/gh/debruine/bfrr?branch=master)
<!-- badges: end -->

Calculate Bayes Factors and robustness regions from summary statistics.

## Installation

You can install the development version from [GitHub](https://github.com/debruine/bfrr) with:

``` r
# install.packages("devtools")
devtools::install_github("debruine/bfrr")
```
## Example


```{r example}
library(bfrr)
```

First, we'll simulate 50 data points from a normal distribution with a mean of 0.25 and SD of 1 and conduct a one-sample t-test.

```{r}
simdat <- rnorm(50, 0.25, 1)
t.test(simdat)
```

Set up the test using `bfrr()`.

```{r}
rr <- bfrr(
  sample_mean = mean(simdat), # mean of the sample
  sample_se = sd(simdat) / sqrt(length(simdat)), # SE of the sample
  sample_df = length(simdat) - 1, # degrees of freedom
  model = "normal",
  mean = 0, # mean of the H1 distribution
  sd = 0.5, # SD of the H1 distribution
  tail = 1, # is the test 1-tailed or 2-tailed
  criterion = 6, # BF against which to test for support for H1/H0
  rr_interval = c(0, 1), # theory_sd over which to explore robustness range
  precision = 2 # number of decimal places to calculate RR
)
```

Use `summary(rr)` to output a summary paragraph.

```{r}
summary(rr)
```

Use `plot(rr)` to view a plot of your data.

```{r}
plot(rr)
```






